\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-30 ASApaper/paper-child.Rnw
more mini comments

All of the parameters we test for significance using the lineup protocol, $\beta_3$ and $\beta_4$, were determined to be statistically significant using Equation~\ref{eq:wald1}. The results from the significance tests we performed using the lineup protocol are given in Table~\ref{tab:sigtesting}

@@

Using the lineup protocol, we show each Amazon Mechanical Turk worker the data once, in a lineup with five other plots of simulated data from one of the models we chose. We examined four different models, M2, M3, M4, and M6, and examined three repititons of each, for a total of 12 goodness-of-fit lineups. In each lineup, the ``null model" is one of the four models and the ``alternative" model is the true, unknown model that generated the senate network data The hypotheses for our goodness-of-fit tests are: 
\begin{description}
\item $H_0$:  The senate network data come from the null model.
\item $H_A$: The senate network data do not come from the null model. 
\end{description}
If a lineup viewer picks out the data among the five simulations from the null model, that is evidence in favor of the alternative hypothesis. On the contrary, if the lineup viewer picks one of the null plots, that is evidence against the alternative hypothsis. Because the size of the lineups is small, the probability of picking the data by chance is high, $\frac{1}{6}$, but if \textit{many} independent viewers pick out the data from the nulls, the evidence in favor of the alternative hypothesis becomes stronger. Results from our MTurk goodness-of-fit plots are provided in Table~\ref{tab:gofstats}.

@@

The $p$-values were calcluated using the \texttt{vinference} package by \citet{vinference}. This package contains methods to calculate \textit{Visual distributions} for lineup experiment data.  The distribution depends on the number of evaluations of a plot, $K$, the size of the lineup, $m$, and the lineup scenario, which here is that each lineup containing the same data and the same set of null plots is shown to $K$ independent observers.  Using these $p$-values, all but one lineup results in a rejection of the null hypothesis at Type-I error rate of $\alpha = 0.05$. The lineup that resulted in a failure to reject the null hypothesis is shown in Figure~\ref{fig:failgof}. The null model in this lineup is M4, and the senate data is shown in panel number $3^2 - 7$, but the panel most chose was number four, and the most common reasoning for that choice was that it had the most simple structure.

@@

>>>>

All of the parameters we test for significance using the lineup protocol, $\beta_3$ and $\beta_4$, were determined to be statistically significant using Equation~\ref{eq:wald1}. The results from the significance tests we performed using the lineup protocol are given in Table~\ref{tab:sigtesting}. \hh{XXX how do we interpret these  visual results? Include the six lineups in an appendix and refer to them from here.}

@@

Using the lineup protocol, we show each Amazon Mechanical Turk worker the data once, in a lineup with five other plots of simulated data from one of the models we chose. We examined four different models, M2, M3, M4, and M6, and examined three repetitions of each, for a total of 12 goodness-of-fit lineups. In each lineup, the ``null model" is one of the four models and the ``alternative" model is the true, unknown model that generated the senate network data. The hypotheses for our goodness-of-fit tests are: 
\begin{description}
\item $H_0$:  The senate network data come from (or could have come from) the null model.
\item $H_A$: The senate network data do not come from the null model. 
\end{description}
If a lineup viewer picks out the data among the five simulations from the null model, it is evidence in favor of the alternative hypothesis. On the contrary, if the lineup viewer picks one of the null plots, that is evidence against the alternative hypothsis. Because the size of the lineups is small, the probability of picking the data by chance is high, $\frac{1}{6}$, but if \textit{many} independent viewers pick out the data from the nulls, the evidence in favor of the alternative hypothesis becomes stronger. Results from our MTurk goodness-of-fit plots are provided in Table~\ref{tab:gofstats}.

@@

The $p$-values were calculated using the \texttt{vinference} package by \citet{vinference}. This package contains methods to calculate \textit{Visual distributions} for lineup experiment data.  The distribution depends on the number of evaluations of a plot, $K$, the size of the lineup, $m$, and the lineup scenario, which here is that each lineup containing the same data and the same set of null plots is shown to $K$ independent observers.  Using these $p$-values, all but one lineup results in a rejection of the null hypothesis at Type-I error rate of $\alpha = 0.05$. The lineup that resulted in a failure to reject the null hypothesis is shown in Figure~\ref{fig:failgof}. The null model in this lineup is M4, and the senate data is shown in panel number $3^2 - 7$. However, the panel most participants chose was number four, and the most common reasoning for that choice was that it had the most simple structure.

@@

\hh{XXX we need to go throught the logic of the argument below.}
